# Sensitivity Analyses: 40%

In the next section we report the sensitivity analyses based on all participants with at least 40% correct responses.

```{r 40%prep, echo = TRUE}
df_analysis14 <- subset(df, df$Surveys.completed >= 14)

#scale independent continuous variables
df_analysis14$StructureForSolitudeIndividualScaled <- scale(df_analysis14$StructureForSolitudeIndividual)
df_analysis14$DayLevelIntentionalitySolitudeScaled <- scale(df_analysis14$DayLevelIntentionalitySolitude)
df_analysis14$DayLevelNatureScaled <- scale(df_analysis14$DayLevelNature)
df_analysis14$DayLevelStructureSolitudeScaled <- scale(df_analysis14$DayLevelStructureSolitude)

df_analysis14$Alone <- as.factor(as.character(df_analysis14$Alone))

df_analysis14_2 <- df_analysis14 %>% select(LowArousalNegativeAffectMean, LowArousalPositiveAffectMean, HighArousalNegativeAffectMean, HighArousalPositiveAffectMean, Alone)
```


## Research Question 1

### Hypothesis 1a
```{r 401a, echo = TRUE}
lme14RQ1d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> converges

#get first summary
summary(lme14RQ1d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ1d , scaled = TRUE)) > 2) / length(resid(lme14RQ1d )) 
sum(abs(resid(lme14RQ1d , scaled = TRUE)) > 2.5) / length(resid(lme14RQ1d )) 
sum(abs(resid(lme14RQ1d , scaled = TRUE)) > 3) / length(resid(lme14RQ1d ))

#2) Homoscedasticity
plot(lme14RQ1d, type = c('p', 'smooth'))
#Looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ1d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ1d, scaled = TRUE))

#Normal enough, but the qqplot some outliers in the tails, small problem

RQ1d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)

RQ1d_p
#effect of alone significant
#positive estimate

#Alone = -1, people = 1
by(df_analysis14_2,df_analysis14_2$Alone, summary)
#check contrasts to verify results
contrasts(df_analysis14$Alone) 


```

Hypothesis 1a is also confirmed for the 40% sensitivity analyses.

### Hypothesis 1b

```{r 401b, echo = TRUE}
lme14RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14) # -> Singular Fit
#1) change to bobyqa
lme14RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) # -> Singular Fit
#2) Turn of gradient and hessian
lme14RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) # -> convergences


#get first summary
summary(lme14RQ1c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ1c , scaled = TRUE)) > 2) / length(resid(lme14RQ1c ))
sum(abs(resid(lme14RQ1c , scaled = TRUE)) > 2.5) / length(resid(lme14RQ1c )) 
sum(abs(resid(lme14RQ1c , scaled = TRUE)) > 3) / length(resid(lme14RQ1c )) 

#2) Homoscedasticity
plot(lme14RQ1c, type = c('p', 'smooth'))
#Looks mostly fine, but strays quite far at the end

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ1c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ1c, scaled = TRUE))

#Normal enough, but the qqplot shows a lot of outliers in the tails, which is quite problematic

RQ1c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
#effect of alone not significant
#Hypothesis 1b not confirmed
RQ1c_p
```

Hypothesis 1b is not confirmed.

### Hypothesis 1c

```{r 401c, echo = TRUE}
lme14RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14) # -> Singular Fit
#1) Change to bobyqa
lme14RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #-> Singular Fit

#2) Turn of gradient and hessian
lme14RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> No Singular Fit warning

#get first summary
summary(lme14RQ1b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ1b , scaled = TRUE)) > 2) / length(resid(lme14RQ1b )) 
sum(abs(resid(lme14RQ1b , scaled = TRUE)) > 2.5) / length(resid(lme14RQ1b )) 
sum(abs(resid(lme14RQ1b , scaled = TRUE)) > 3) / length(resid(lme14RQ1b ))

#2) Homoscedasticity
plot(lme14RQ1b, type = c('p', 'smooth'))
#Looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ1b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ1b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
RQ1b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
#Effect of Alone is significant
RQ1b_p
#get means
df_analysis14_2 <- df_analysis14 %>% select(LowArousalNegativeAffectMean, LowArousalPositiveAffectMean, HighArousalNegativeAffectMean, HighArousalPositiveAffectMean, Alone)
#estimate is positive, mean is lower for alone == 1, hence people have higher levels of lowarousalpositive affect when they are among people
by(df_analysis14_2,df_analysis14_2$Alone, summary)

#check contrasts to verify results
contrasts(df_analysis14$Alone) 
#Alone = -1, People = 1, 

#Positive Fixed Effect, hence it fits with the means.
#Hypothesis 1C not confirmed, effect in the opposite direction.

```

Hypothesis 1C is not confirmed. In contrast, here the effect also goes into the opposite direction.

### Hypothesis 1d

```{r 401d, echo = TRUE}
lme14RQ1 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14)

#get first summary
summary(lme14RQ1)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ1 , scaled = TRUE)) > 2) / length(resid(lme14RQ1 )) 
sum(abs(resid(lme14RQ1 , scaled = TRUE)) > 2.5) / length(resid(lme14RQ1 ))
sum(abs(resid(lme14RQ1 , scaled = TRUE)) > 3) / length(resid(lme14RQ1 ))

#2) Homoscedasticity
plot(lme14RQ1, type = c('p', 'smooth'))
#Also somewhat violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ1, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ1, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails

RQ1_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis14, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1_p
#The effect of Alone is not significant. 
#Hypothesis 1D is not supported.

```

Hypothesis 1D is not supported.

### Correction for Multiple Testing

Next we check whether these effects also hold after correction for multiple testing.

```{r 40mt, echo = TRUE}
df_analysis14RQ1_pvalues <- as.data.frame(rbind(RQ1_p$anova_table$`Pr(>F)`, RQ1b_p$anova_table$`Pr(>F)`, RQ1c_p$anova_table$`Pr(>F)`, RQ1d_p$anova_table$`Pr(>F)`))

df_analysis14RQ1_pvalues$adjusted <- p.adjust(df_analysis14RQ1_pvalues$V2, method = "holm")
#1A is also confirmed after correction, whereas the effect in the opposite direction at 1C disappears.

df_analysis14RQ1_pvalues$adjusted
```

Only Hypothesis 1a is confirmed after correction for multiple testing. The effect observed at 1C disappears.

## Research Question 2

### Hypotheses 2Aa and 2Bc

```{r 402a, echo = TRUE}
lme14RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 


#get first summary
summary(lme14RQ2d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ2d , scaled = TRUE)) > 2) / length(resid(lme14RQ2d ))
sum(abs(resid(lme14RQ2d , scaled = TRUE)) > 2.5) / length(resid(lme14RQ2d ))
sum(abs(resid(lme14RQ2d , scaled = TRUE)) > 3) / length(resid(lme14RQ2d ))

#2) Homoscedasticity
plot(lme14RQ2d, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ2d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ2d, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ2d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2d_p 
#2Aa not supported. "Support" for 2Bc/d because we predicted no effect and there is no effect
#Significant effect of Alone

```

Hypothesis 2Aa is not supported. However, as expected, we find no significant interaction effect (2Bc)

### Hypotheses 2Ab and 2Bd

```{r 402Aa, echo = TRUE}
lme14RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 


#get first summary
summary(lme14RQ2c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ2c , scaled = TRUE)) > 2) / length(resid(lme14RQ2c )) 
sum(abs(resid(lme14RQ2c , scaled = TRUE)) > 2.5) / length(resid(lme14RQ2c )) 
sum(abs(resid(lme14RQ2c , scaled = TRUE)) > 3) / length(resid(lme14RQ2c ))

#2) Homoscedasticity
plot(lme14RQ2c, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ2c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ2c, scaled = TRUE))

#Barely Normal and the qqplot shows quite some outliers in the tails

RQ2c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2c_p 
#2Ab not supported. 2Bc/d "supported", as in we did not predict an effect and we did not observe an effect
```

Hypothesis 2Ab is not supported. However, as expected, we observed no interaction (2Bd).

### Hypotheses 2Ac and 2Ba

```{r 402Ac, echo = TRUE}
lme14RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges and produces negative eigenvalues in the calculation of p-values. 

lme14RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone + DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme14RQ2b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ2b , scaled = TRUE)) > 2) / length(resid(lme14RQ2b )) 
sum(abs(resid(lme14RQ2b , scaled = TRUE)) > 2.5) / length(resid(lme14RQ2b )) 
sum(abs(resid(lme14RQ2b , scaled = TRUE)) > 3) / length(resid(lme14RQ2b ))

#2) Homoscedasticity
plot(lme14RQ2b, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ2b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ2b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails
RQ2b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone + DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2b_p
#2Ac amd 2Ba not supported
```

Hypothesis 2Ac and hypothesis 2Ba are not supported.

### Hypotheses 2Ad and 2Bb

```{r 402Ad, echo = TRUE}
lme14RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme14RQ2)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ2 , scaled = TRUE)) > 2) / length(resid(lme14RQ2 )) 
sum(abs(resid(lme14RQ2 , scaled = TRUE)) > 2.5) / length(resid(lme14RQ2 )) 
sum(abs(resid(lme14RQ2 , scaled = TRUE)) > 3) / length(resid(lme14RQ2 )) 

#2) Homoscedasticity
plot(lme14RQ2, type = c('p', 'smooth'))
#Trails off strongly in the tails

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ2, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ2, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails

RQ2_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ2_p 
#no significant hypothesized effects, 
#Hypothesis 2Ad and 2Bb not supported
```

Hypothesis 2Ad and hypothesis 2Bb are not supported.

## Research Question 3

### Hypotheses 3Aa and 3Bc

```{r 403Aa, echo = TRUE}

lme14RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #warning

lme14RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa"), data = df_analysis14) #warning

lme14RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14) #converges


#get first summary
summary(lme14RQ3d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ3d , scaled = TRUE)) > 2) / length(resid(lme14RQ3d )) 
sum(abs(resid(lme14RQ3d , scaled = TRUE)) > 2.5) / length(resid(lme14RQ3d )) 
sum(abs(resid(lme14RQ3d , scaled = TRUE)) > 3) / length(resid(lme14RQ3d ))

#2) Homoscedasticity
plot(lme14RQ3d, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ3d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ3d, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ3d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))
RQ3d_p
#3Aa not supported. 3Bc/d: No interaction
```

Hypothesis 3Aa is not supported. However, as expected, there is no interaction (3Bc).

### Hypotheses 3Ab and 3Bd

```{r 403ab, echo = TRUE}

lme14RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges




#get first summary
summary(lme14RQ3c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ3c , scaled = TRUE)) > 2) / length(resid(lme14RQ3c )) 
sum(abs(resid(lme14RQ3c , scaled = TRUE)) > 2.5) / length(resid(lme14RQ3c )) 
sum(abs(resid(lme14RQ3c , scaled = TRUE)) > 3) / length(resid(lme14RQ3c )) 

#2) Homoscedasticity
plot(lme14RQ3c, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ3c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ3c, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ3c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3c_p
#3Ab not supported, 3Bc/d: No interaction
```

Hypothesis 3Ab is not supported. However, as expected, we observed no interaction (3Bd).

### Hypotheses 3Ac and 3Ba

```{r 403Ac, echo = TRUE}

lme14RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but produces negative eigenvalue in p-value calculation

lme14RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone+DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) # -> converges



#get first summary
summary(lme14RQ3b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ3b , scaled = TRUE)) > 2) / length(resid(lme14RQ3b )) 
sum(abs(resid(lme14RQ3b , scaled = TRUE)) > 2.5) / length(resid(lme14RQ3b )) 
sum(abs(resid(lme14RQ3b , scaled = TRUE)) > 3) / length(resid(lme14RQ3b )) 

#2) Homoscedasticity
plot(lme14RQ3b, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ3b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ3b, scaled = TRUE))

#qqplot shows some outliers in the tails
RQ3b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone+DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#3Ac and 3Ba not supported
RQ3b_p

```

Hypotheses 3Ac and 3Ba are not supported.

### Hypotheses 3Ad and 3Bb

```{r 403Ad, echo = TRUE}

lme14RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 


#get first summary
summary(lme14RQ3)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ3 , scaled = TRUE)) > 2) / length(resid(lme14RQ3 )) 
sum(abs(resid(lme14RQ3 , scaled = TRUE)) > 2.5) / length(resid(lme14RQ3 )) 
sum(abs(resid(lme14RQ3 , scaled = TRUE)) > 3) / length(resid(lme14RQ3 ))
#2) Homoscedasticity
plot(lme14RQ3, type = c('p', 'smooth'))
#skewed in the right tail

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ3, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ3, scaled = TRUE))

#qqplot shows quite some outliers in the tails

RQ3_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3_p
#3Ad and 3Bb not supported

```

Hypotheses 3Ad and 3Bb are not supported.

## Research Question 4

### Hypotheses 4Aa and 4Ba Day-Level

```{r 404Aday, echo = TRUE}
lme14RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges



#get first summary
summary(lme14RQ4d.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4d.day , scaled = TRUE)) > 2) / length(resid(lme14RQ4d.day )) 
sum(abs(resid(lme14RQ4d.day , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4d.day ))  
sum(abs(resid(lme14RQ4d.day , scaled = TRUE)) > 3) / length(resid(lme14RQ4d.day ))

#2) Homoscedasticity
plot(lme14RQ4d.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4d.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4d.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4d.day_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ4d.day_p 
#Hypothesis 4Aa and 4Ba day not supported
```
Hypotheses 4Aa and 4Ba day-level are not supported.

### Hypotheses 4Ab and 4Bb Day-Level

```{r 404Abday, echo = TRUE}


lme14RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges



#get first summary
summary(lme14RQ4c.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4c.day , scaled = TRUE)) > 2) / length(resid(lme14RQ4c.day ))
sum(abs(resid(lme14RQ4c.day , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4c.day ))  
sum(abs(resid(lme14RQ4c.day , scaled = TRUE)) > 3) / length(resid(lme14RQ4c.day ))

#2) Homoscedasticity
plot(lme14RQ4c.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4c.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4c.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4c.day_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ab and 4Bb day not supported
RQ4c.day_p
```

Hypotheses 4Ab and 4Bb day-level are not supported.

### Hypotheses 4Ac and 4Bc Day-Level

```{r 404Acday, echo = TRUE}

lme14RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #->not

lme14RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14,  control = lmerControl(optimizer = "bobyqa")) # not

lme14RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14,  control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges

#get first summary
summary(lme14RQ4b.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4b.day , scaled = TRUE)) > 2) / length(resid(lme14RQ4b.day )) 
sum(abs(resid(lme14RQ4b.day , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4b.day )) 
sum(abs(resid(lme14RQ4b.day , scaled = TRUE)) > 3) / length(resid(lme14RQ4b.day )) 

#2) Homoscedasticity
plot(lme14RQ4b.day, type = c('p', 'smooth'))
#looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4b.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4b.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails

RQ4b.day_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis14, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ4b.day_p
#Hypothesis 4Ac day not supported, 4Bc/d: No Interaction
```

Hypothesis 4Ac day is not supported. However, as expected, there is no interaction (4Bc).

### Hypotheses 4Ad and 4Bd Day-Level

```{r 404Adday, echo = TRUE}

lme14RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme14RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme14RQ4.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4.day , scaled = TRUE)) > 2) / length(resid(lme14RQ4.day ))
sum(abs(resid(lme14RQ4.day , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4.day ))  
sum(abs(resid(lme14RQ4.day , scaled = TRUE)) > 3) / length(resid(lme14RQ4.day ))

#2) Homoscedasticity
plot(lme14RQ4.day, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4.day_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ad day not supported, 4Bc/d: No Interaction
RQ4.day_p 
```

Hypothesis 4Ad day-level is not supported. However, as expected, there is no interaction (4Bd).

### Hypotheses 4Aa and 4Ba Person-Level

```{r 404aperson, echo = TRUE}
lme14RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme14RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalue

lme14RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))

#get first summary
summary(lme14RQ4d.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4d.individual , scaled = TRUE)) > 2) / length(resid(lme14RQ4d.individual )) 
sum(abs(resid(lme14RQ4d.individual , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4d.individual )) 
sum(abs(resid(lme14RQ4d.individual , scaled = TRUE)) > 3) / length(resid(lme14RQ4d.individual ))

#2) Homoscedasticity
plot(lme14RQ4d.individual, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4d.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4d.individual, scaled = TRUE))

#qqplot shows outliers in the tails

RQ4d.individual_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)
RQ4d.individual_p
#Hypothesis 4Aa and 4Ba not suported
```

Hypotheses 4Aa and 4Ba person-level are not supported.

### Hypotheses 4Ab and 4Bb Person-Level

```{r 404Abperson, echo = TRUE}
lme14RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme14RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges



#get first summary
summary(lme14RQ4c.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4c.individual , scaled = TRUE)) > 2) / length(resid(lme14RQ4c.individual )) 
sum(abs(resid(lme14RQ4c.individual , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4c.individual )) 
sum(abs(resid(lme14RQ4c.individual , scaled = TRUE)) > 3) / length(resid(lme14RQ4c.individual ))

#2) Homoscedasticity
plot(lme14RQ4c.individual, type = c('p', 'smooth'))
#looks slightly violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4c.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4c.individual, scaled = TRUE))

#qqplot shows strong outliers in the tails

#RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)

#Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl für Funktion 'forceSymmetric': System ist für den Rechner singulär: reziproke Konditionszahl = 1.1049e-33

RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S",  cl = MyCluster)
RQ4c.individual_p 
```

Hypotheses 4Ab is not supported. However, there is a significant interaction (pending verification after multiple testing).

### Hypotheses 4Ac and 4Bc Person-Level

```{r 404Acperson, echo = TRUE}
lme14RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme14RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalue

lme14RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))


#get first summary
summary(lme14RQ4b.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4b.individual , scaled = TRUE)) > 2) / length(resid(lme14RQ4b.individual )) 
sum(abs(resid(lme14RQ4b.individual , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4b.individual )) 
sum(abs(resid(lme14RQ4b.individual , scaled = TRUE)) > 3) / length(resid(lme14RQ4b.individual ))

#2) Homoscedasticity
plot(lme14RQ4b.individual, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4b.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4b.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#RQ4b.individual_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl für Funktion 'forceSymmetric': System ist für den Rechner singulär: reziproke Konditionszahl = 5.36477e-36

RQ4b.individual_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S",  cl = MyCluster, expand_re = TRUE)
#Hypothesis 4Ac individual not supported, 4Bc/d: No Interaction
RQ4b.individual_p 
```

Hypothesis 4Ac person-level is not supported. However, there is a significant interaction (contrary to expectations 4Bc).

### Hypotheses 4Ad and 4Bd Person-Level

```{r 404adperson, echo = TRUE}


lme14RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14) #-> does not convergence

lme14RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme14RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but shows eigenvalue issues

lme14RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone+StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))

#get first summary
summary(lme14RQ4.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme14RQ4.individual , scaled = TRUE)) > 2) / length(resid(lme14RQ4.individual ))
sum(abs(resid(lme14RQ4.individual , scaled = TRUE)) > 2.5) / length(resid(lme14RQ4.individual )) 
sum(abs(resid(lme14RQ4.individual , scaled = TRUE)) > 3) / length(resid(lme14RQ4.individual )) 

#2) Homoscedasticity
plot(lme14RQ4.individual, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme14RQ4.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme14RQ4.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4.individual_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone+StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis14, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ad individual not supported, 4Bc/d: No Interaction
RQ4.individual_p 
```

Hypothesis 4Ad person-level is not supported. However, as expected, there was no interaction (4Ad).


### Correction for Multiple Testing
```{r 4ApersonMT, echo = TRUE}
df_analysis14RQ4_person_pvalues <- as.data.frame(rbind(RQ4.individual_p$anova_table$`Pr(>F)`[4], RQ4b.individual_p$anova_table$`Pr(>F)`[3], RQ4c.individual_p$anova_table$`Pr(>F)`[3], RQ4d.individual_p$anova_table$`Pr(>F)`[4]))

df_analysis14RQ4_person_pvalues$adjusted <- p.adjust(df_analysis14RQ4_person_pvalues$V1, method = "holm")
df_analysis14RQ4_person_pvalues$adjusted
```

After correction, no significant p-values remain.