# Sensitivity Analyses: 60%

In the next section we report the sensitivity analyses based on all participants with at least 60% correct responses.

```{r 60%prep, echo = TRUE}
df_analysis21 <- subset(df, df$Surveys.completed >= 21)

#scale independent continuous variables
df_analysis21$StructureForSolitudeIndividualScaled <- scale(df_analysis21$StructureForSolitudeIndividual)
df_analysis21$DayLevelIntentionalitySolitudeScaled <- scale(df_analysis21$DayLevelIntentionalitySolitude)
df_analysis21$DayLevelNatureScaled <- scale(df_analysis21$DayLevelNature)
df_analysis21$DayLevelStructureSolitudeScaled <- scale(df_analysis21$DayLevelStructureSolitude)

df_analysis21$Alone <- as.factor(as.character(df_analysis21$Alone))


df_analysis21_2 <- df_analysis21 %>% select(LowArousalNegativeAffectMean, LowArousalPositiveAffectMean, HighArousalNegativeAffectMean, HighArousalPositiveAffectMean, Alone)
```


## Research Question 1

### Hypothesis 1a
```{r 601a, echo = TRUE}
lme21RQ1d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> converges

#get first summary
summary(lme21RQ1d)




#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 2) / length(resid(lme21RQ1d ))
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1d )) 
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 3) / length(resid(lme21RQ1d )) 

#2) Homoscedasticity
plot(lme21RQ1d, type = c('p', 'smooth'))
#Looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1d, scaled = TRUE))

#Normal enough, but the qqplot some outliers in the tails, small problem

RQ1d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1d_p
#effect of alone significant
#positive estimate


by(df_analysis21_2,df_analysis21_2$Alone, summary)
#check contrasts to verify results
contrasts(df_analysis21$Alone) 

#Hypothesis 1A confirmed



```

Hypothesis 1a is also confirmed for the 60% sensitivity analyses.

### Hypothesis 1b

```{r 601b, echo = TRUE}
lme21RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21)

#get first summary
summary(lme21RQ1c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 2) / length(resid(lme21RQ1c )) 
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1c )) 
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 3) / length(resid(lme21RQ1c )) 

#2) Homoscedasticity
plot(lme21RQ1c, type = c('p', 'smooth'))
#Looks mostly fine, but strays quite far at the end

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1c, scaled = TRUE))

#Normal enough, but the qqplot shows a lot of outliers in the tails, which is quite problematic
#Calculate p-values
RQ1c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1c_p
#effect of alone not significant
#Hypothesis 1b not confirmed
```

Hypothesis 1b is not confirmed.

### Hypothesis 1c

```{r 601c, echo = TRUE}
lme21RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21) 

#get first summary
summary(lme21RQ1b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 2) / length(resid(lme21RQ1b )) 
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1b )) 
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 3) / length(resid(lme21RQ1b )) 

#2) Homoscedasticity
plot(lme21RQ1b, type = c('p', 'smooth'))
#Looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails

RQ1b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1b_p 
#Effect of Alone is significant
by(df_analysis21_2,df_analysis21_2$Alone, summary)

#check contrasts to verify results
contrasts(df_analysis21$Alone) 

#Hypothesis 1C not confirmed, effect in the opposite direction.


```

Hypothesis 1C is not confirmed. In contrast, here the effect also goes into the opposite direction.

### Hypothesis 1d

```{r 601d, echo = TRUE}
lme21RQ1 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21)

#get first summary
summary(lme21RQ1)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 2) / length(resid(lme21RQ1 ))
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1 ))
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 3) / length(resid(lme21RQ1 ))

#2) Homoscedasticity
plot(lme21RQ1, type = c('p', 'smooth'))
#Also somewhat violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
RQ1_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)

#Hypothesis 1D is not supported.
RQ1_p


```

Hypothesis 1D is also still supported.

### Correction for Multiple Testing

Next we check whether these effects also hold after correction for multiple testing.

```{r 60mt, echo = TRUE}

df_analysis21RQ1_pvalues <- as.data.frame(rbind(RQ1_p$anova_table$`Pr(>F)`, RQ1b_p$anova_table$`Pr(>F)`, RQ1c_p$anova_table$`Pr(>F)`, RQ1d_p$anova_table$`Pr(>F)`))

df_analysis21RQ1_pvalues$adjusted <- p.adjust(df_analysis21RQ1_pvalues$V2, method = "holm")


df_analysis21RQ1_pvalues$adjusted
```

Hypothesis 1a and 1d are confirmed after correction for multiple testing. The effect observed at 1C also remains significant after correction for multiple testing.

## Research Question 2

### Hypotheses 2Aa and 2Bc

```{r 602a, echo = TRUE}
lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 

#get first summary
summary(lme21RQ2d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 2) / length(resid(lme21RQ2d )) 
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2d )) 
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 3) / length(resid(lme21RQ2d )) 

#2) Homoscedasticity
plot(lme21RQ2d, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2d, scaled = TRUE))

#qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2d_p <- afex::mixed(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2d_p 
#2Aa not supported. "Support" for 2Bc/d because we predicted no effect and there is no effect
#Significant effect of Alone
```

Hypothesis 2Aa is not supported. However, as expected, we find no significant interaction effect (2Bc)

### Hypotheses 2Ab and 2Bd

```{r 602Aa, echo = TRUE}

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges
summary(lme21RQ2c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 2) / length(resid(lme21RQ2c ))
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2c )) 
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 3) / length(resid(lme21RQ2c )) 

#2) Homoscedasticity
plot(lme21RQ2c, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2c, scaled = TRUE))

#Barely Normal and the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2c_p 
#2Ab not supported. 2Bc/d "supported", as in we did not predict an effect and we did not observe an effect

```

Hypothesis 2Ab is not supported. However, as expected, we observed no interaction (2Bd).

### Hypotheses 2Ac and 2Ba

```{r 602Ac, echo = TRUE}
lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 

#get first summary
summary(lme21RQ2b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 2) / length(resid(lme21RQ2b )) 
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2b )) 
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 3) / length(resid(lme21RQ2b ))

#2) Homoscedasticity
plot(lme21RQ2b, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ2b_p
#2Ac and 2Ba not supported

```

Hypothesis 2Ac and hypothesis 2Ba are not supported.

### Hypotheses 2Ad and 2Bb

```{r 602Ad, echo = TRUE}

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ2)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 2) / length(resid(lme21RQ2 )) 
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2 )) 
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 3) / length(resid(lme21RQ2 ))

#2) Homoscedasticity
plot(lme21RQ2, type = c('p', 'smooth'))
#Trails off strongly in the tails

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ2_p
#no significant hypothesized effects, 
#Hypothesis 2Ad and 2Bb not supported
```

Hypothesis 2Ad and hypothesis 2Bb are not supported.

## Research Question 3

### Hypotheses 3Aa and 3Bc

```{r 603Aa, echo = TRUE}

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #does not converge

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa"), data = df_analysis21) #does not converge

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21) #converges

#get first summary
summary(lme21RQ3d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 2) / length(resid(lme21RQ3d )) 
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3d ))
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 3) / length(resid(lme21RQ3d ))

#2) Homoscedasticity
plot(lme21RQ3d, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3d, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3d_p 

```

Hypothesis 3Aa is not supported. However, as expected, there is no interaction (3Bc).

### Hypotheses 3Ab and 3Bd

```{r 603ab, echo = TRUE}

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges




#get first summary
summary(lme21RQ3c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 2) / length(resid(lme21RQ3c )) 
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3c ))
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 3) / length(resid(lme21RQ3c ))

#2) Homoscedasticity
plot(lme21RQ3c, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3c, scaled = TRUE))

#qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#3Ab not supported, 3Bc/d: No interaction
RQ3c_p 
```

Hypothesis 3Ab is not supported. However, as expected, we observed no interaction (3Bd).

### Hypotheses 3Ac and 3Ba

```{r 603Ac, echo = TRUE}

lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) 

#get first summary
summary(lme21RQ3b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 2) / length(resid(lme21RQ3b ))
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3b )) 
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 3) / length(resid(lme21RQ3b ))

#2) Homoscedasticity
plot(lme21RQ3b, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3b, scaled = TRUE))

#qqplot shows some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3b_p 
#3Ac and 3Ba not supported

```

Hypotheses 3Ac and 3Ba are not supported.

### Hypotheses 3Ad and 3Bb

```{r 603Ad, echo = TRUE}

lme21RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) 

#get first summary
summary(lme21RQ3)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 2) / length(resid(lme21RQ3 )) 
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3 )) 
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 3) / length(resid(lme21RQ3 )) 

#2) Homoscedasticity
plot(lme21RQ3, type = c('p', 'smooth'))
#skewed in the right tail

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#3Ad and 3Bb not supported
RQ3_p 
```

Hypotheses 3Ad and 3Bb are not supported.

## Research Question 4

### Hypotheses 4Aa and 4Ba Day-Level

```{r 604Aday, echo = TRUE}
lme21RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) 

#get first summary
summary(lme21RQ4d.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4d.day )) 
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4d.day ))
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4d.day )) 
#2) Homoscedasticity
plot(lme21RQ4d.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4d.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4d.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4d.day_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Aa and 4Ba day not supported
RQ4d.day_p 
```
Hypotheses 4Aa and 4Ba day-level are not supported.

### Hypotheses 4Ab and 4Bb Day-Level

```{r 604Abday, echo = TRUE}


lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges



#get first summary
summary(lme21RQ4c.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4c.day ))
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4c.day )) 
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4c.day ))
#2) Homoscedasticity
plot(lme21RQ4c.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4c.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4c.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ4c.day_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ab and 4Bb day not supported
RQ4c.day_p
```

Hypotheses 4Ab and 4Bb day-level are not supported.

### Hypotheses 4Ac and 4Bc Day-Level

```{r 604Acday, echo = TRUE}

lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not converge

#
lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa"), data = df_analysis21) #-> does not converge


lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay),control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21) #-> converges


#get first summary
summary(lme21RQ4b.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4b.day )) 
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4b.day )) 
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4b.day )) 

#2) Homoscedasticity
plot(lme21RQ4b.day, type = c('p', 'smooth'))
#looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4b.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4b.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ4b.day_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay),control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ac day not supported, 4Bc/d: No Interaction
RQ4b.day_p

```

Hypothesis 4Ac day is not supported. However, as expected, there is no interaction (4Bc).

### Hypotheses 4Ad and 4Bd Day-Level

```{r 604Adday, echo = TRUE}

lme21RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) 


#get first summary
summary(lme21RQ4.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4.day ))
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4.day )) 
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4.day ))

#2) Homoscedasticity
plot(lme21RQ4.day, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails

RQ4.day_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21,  type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ad day not supported, 4Bc/d: No Interaction
RQ4.day_p 
```

Hypothesis 4Ad day-level is not supported. However, as expected, there is no interaction (4Bd).

### Hypotheses 4Aa and 4Ba Person-Level

```{r 604aperson, echo = TRUE}
lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) 

#get first summary
summary(lme21RQ4d.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4d.individual ))
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4d.individual ))  
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4d.individual ))

#2) Homoscedasticity
plot(lme21RQ4d.individual, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4d.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4d.individual, scaled = TRUE))

#qqplot shows outliers in the tails

RQ4d.individual_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa",  calc.derivs = FALSE), type = 3, method = "KR",  test_intercept = TRUE,  cl = MyCluster)
RQ4d.individual_p
#Hypothesis 4Aa and 4Ba not suported
```

Hypotheses 4Aa and 4Ba person-level are not supported.

### Hypotheses 4Ab and 4Bb Person-Level

```{r 604Abperson, echo = TRUE}
lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges




#get first summary
summary(lme21RQ4c.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4c.individual )) 
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4c.individual ))
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4c.individual )) 
#2) Homoscedasticity
plot(lme21RQ4c.individual, type = c('p', 'smooth'))
#looks slightly violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4c.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4c.individual, scaled = TRUE))

#qqplot shows strong outliers in the tails
#RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Fehler in h(simpleError(msg, call)) : 
#Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl f체r Funktion 'forceSymmetric': Lapackroutine dgesv: System ist genau singul채r: U[12,12] = 0

RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S",  cl = MyCluster)
RQ4c.individual_p 
```

Hypotheses 4Ab and 4Bb are not supported. 

### Hypotheses 4Ac and 4Bc Person-Level

```{r 604Acperson, echo = TRUE}
lme21RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) 

#get first summary
summary(lme21RQ4b.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4b.individual ))
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4b.individual ))  
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4b.individual ))

#2) Homoscedasticity
plot(lme21RQ4b.individual, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4b.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4b.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails


RQ4b.individual_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE,  cl = MyCluster)
RQ4b.individual_p
#Hypothesis 4Ac individual not supported, 4Bc/d: No Interaction
```

Hypothesis 4Ac person-level is not supported. However, there is no significant interaction (as expected 4Bc).

### Hypotheses 4Ad and 4Bd Person-Level

```{r 604adperson, echo = TRUE}

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) 

#get first summary
summary(lme21RQ4.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4.individual )) 
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4.individual ))
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4.individual ))

#2) Homoscedasticity
plot(lme21RQ4.individual, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
#RQ4.individual_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)

#Fehler in h(simpleError(msg, call)) : Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl f체r Funktion 'forceSymmetric': Lapackroutine dgesv: System ist genau singul채r: U[12,12] = 0


RQ4.individual_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S", cl = MyCluster)

#Hypothesis 4Ad individual not supported, 4Bc/d: No Interaction
RQ4.individual_p 
```

Hypothesis 4Ad person-level is not supported. Moreover, as expected, there was no interaction (4Ad).



## Exploratory Research Questions

### Preparation

Here we prepare the 60% sensitivity analysis of the exploratory research question

```{r RQ560prep, echo = TRUE}

#create lagged alone variable as preparation for creating the epoch variable
df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(AloneLagged = dplyr::lag(Alone, n = 1, default = NA))

#create epoch. epoch = 1 if alone & alone lagged are not equal and not NA.
df_analysis21 <- 
  df_analysis21 %>%
  mutate(epoch = ifelse(Alone == 1 & AloneLagged == 0 | Alone == 0 & AloneLagged == 1, 1, 0)) 

df_analysis21$epoch <- as.factor(as.character(df_analysis21$epoch))

#create affect.0 variables, which are the lagged versions of the affect variables.
df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(LowArousalNegativeAffectMeanLagged = dplyr::lag(LowArousalNegativeAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(LowArousalPositiveAffectMeanLagged = dplyr::lag(LowArousalPositiveAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(HighArousalNegativeAffectMeanLagged = dplyr::lag(HighArousalNegativeAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(HighArousalPositiveAffectMeanLagged = dplyr::lag(HighArousalPositiveAffectMean, n = 1, default = NA))

#scale the lagged variable as predictor

df_analysis21$LowArousalNegativeAffectMeanLaggedScaled <- scale(df_analysis21$LowArousalNegativeAffectMeanLagged)

df_analysis21$LowArousalPositiveAffectMeanLaggedScaled <- scale(df_analysis21$LowArousalPositiveAffectMeanLagged)

df_analysis21$HighArousalNegativeAffectMeanLaggedScaled <- scale(df_analysis21$HighArousalNegativeAffectMeanLagged)

df_analysis21$HighArousalPositiveAffectMeanLaggedScaled <- scale(df_analysis21$HighArousalPositiveAffectMeanLagged)
```


### Analyses

Next, we perform all four analysis and perform a correction for multiple testing where necessary.

```{r RQ560analysis, echo = TRUE}
#####fit mixed model#####
##LowArousalNegative Affect##
lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence


lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) # does not converge

lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) #converges, but eigenvalue issues

lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)))

#get first summary
summary(lme21RQ5)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 2) / length(resid(lme21RQ5 ))
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5 )) 
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 3) / length(resid(lme21RQ5 )) 

#2) Homoscedasticity
plot(lme21RQ5, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values
#says the predictor is not centered on zero
RQ5_p <- afex::mixed (LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster) #failed to converge with negative eigenvalue

RQ5_p <- afex::mixed (LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)

RQ5_p


##low arousal positive affect##
#####fit mixed model#####
lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 

#get first summary
summary(lme21RQ5b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 2) / length(resid(lme21RQ5b ))
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5b )) 
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 3) / length(resid(lme21RQ5b )) 

#2) Homoscedasticity
plot(lme21RQ5b, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5b, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5b_p <- afex::mixed (LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ5b_p


##high arousal negative affect##
#####fit mixed model#####
lme21RQ5c <- lme4::lmer(HighArousalNegativeAffectMean ~ HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5c <- lme4::lmer(HighArousalNegativeAffectMean ~ HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5c <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 

#get first summary
summary(lme21RQ5c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 2) / length(resid(lme21RQ5c ))
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5c )) 
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 3) / length(resid(lme21RQ5c )) 

#2) Homoscedasticity
plot(lme21RQ5c, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5c, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5c_p <- afex::mixed(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ5c_p


##high arousal positive affect##

#####fit mixed model#####
lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 

#get first summary
summary(lme21RQ5d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 2) / length(resid(lme21RQ5d ))
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5d )) 
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 3) / length(resid(lme21RQ5d )) 

#2) Homoscedasticity
plot(lme21RQ5d, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5d, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5d_p <- afex::mixed(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ5d_p


#Adjust effect of affect.0 variables
df_analysis21RQ5.2_pvalues <- as.data.frame(rbind(RQ5_p$anova_table$`Pr(>F)`[2], RQ5b_p$anova_table$`Pr(>F)`[2], RQ5c_p$anova_table$`Pr(>F)`[2], RQ5d_p$anova_table$`Pr(>F)`[2]))

df_analysis21RQ5.2_pvalues$adjusted <- p.adjust(df_analysis21RQ5.2_pvalues$V1, method = "holm")
df_analysis21RQ5.2_pvalues$adjusted #all remain significant

#adjust for alone : epoch interaction
df_analysis21RQ5.7_pvalues <- as.data.frame(rbind(RQ5_p$anova_table$`Pr(>F)`[7], RQ5b_p$anova_table$`Pr(>F)`[7], RQ5c_p$anova_table$`Pr(>F)`[7], RQ5d_p$anova_table$`Pr(>F)`[7]))

df_analysis21RQ5.7_pvalues$adjusted <- p.adjust(df_analysis21RQ5.7_pvalues$V1, method = "holm")
df_analysis21RQ5.7_pvalues$adjusted #one remains significant.


## Exploratory Research Questions

### Preparation



#create lagged alone variable as preparation for creating the epoch variable
df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(AloneLagged = dplyr::lag(Alone, n = 1, default = NA))

#create epoch. epoch = 1 if alone & alone lagged are not equal and not NA.
df_analysis21 <- 
  df_analysis21 %>%
  mutate(epoch = ifelse(Alone == 1 & AloneLagged == 0 | Alone == 0 & AloneLagged == 1, 1, 0)) 

df_analysis21$epoch <- as.factor(as.character(df_analysis21$epoch))

#create affect.0 variables, which are the lagged versions of the affect variables.
df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(LowArousalNegativeAffectMeanLagged = dplyr::lag(LowArousalNegativeAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(LowArousalPositiveAffectMeanLagged = dplyr::lag(LowArousalPositiveAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(HighArousalNegativeAffectMeanLagged = dplyr::lag(HighArousalNegativeAffectMean, n = 1, default = NA))

df_analysis21 <- 
  df_analysis21 %>%
  group_by(Participant.ID) %>%
  mutate(HighArousalPositiveAffectMeanLagged = dplyr::lag(HighArousalPositiveAffectMean, n = 1, default = NA))

#scale the lagged variable as predictor

df_analysis21$LowArousalNegativeAffectMeanLaggedScaled <- scale(df_analysis21$LowArousalNegativeAffectMeanLagged)

df_analysis21$LowArousalPositiveAffectMeanLaggedScaled <- scale(df_analysis21$LowArousalPositiveAffectMeanLagged)

df_analysis21$HighArousalNegativeAffectMeanLaggedScaled <- scale(df_analysis21$HighArousalNegativeAffectMeanLagged)

df_analysis21$HighArousalPositiveAffectMeanLaggedScaled <- scale(df_analysis21$HighArousalPositiveAffectMeanLagged)




#####fit mixed model#####
##LowArousalNegative Affect##
lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence


lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) # does not converge

lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) #converges, but eigenvalue issues

lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) #still eigenvalue issues

lme21RQ5 <- lme4::lmer(LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled+Alone+epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 


#get first summary
summary(lme21RQ5)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 2) / length(resid(lme21RQ5 ))
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5 )) 
sum(abs(resid(lme21RQ5 , scaled = TRUE)) > 3) / length(resid(lme21RQ5 )) 

#2) Homoscedasticity
plot(lme21RQ5, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values
#says the predictor is not centered on zero
#RQ5_p <- afex::mixed (LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster) #failed to converge with negative eigenvalue

#RQ5_p <- afex::mixed (LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster) #failed to converge with negative eigenvalue


RQ5_p <- afex::mixed (LowArousalNegativeAffectMean ~ LowArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalNegativeAffectMeanLaggedScaled+Alone+epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)

RQ5_p


##low arousal positive affect##
#####fit mixed model#####
lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5b <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 

#get first summary
summary(lme21RQ5b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 2) / length(resid(lme21RQ5b ))
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5b )) 
sum(abs(resid(lme21RQ5b , scaled = TRUE)) > 3) / length(resid(lme21RQ5b )) 

#2) Homoscedasticity
plot(lme21RQ5b, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5b, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5b_p <- afex::mixed (LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ5b_p


 ##high arousal negative affect##
#####fit mixed model#####
lme21RQ5c <- lme4::lmer(HighArousalNegativeAffectMean ~ HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5c <- lme4::lmer(HighArousalNegativeAffectMean ~ HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalNegativeAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5c <- lme4::lmer(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) 

#get first summary
summary(lme21RQ5c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 2) / length(resid(lme21RQ5c ))
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5c )) 
sum(abs(resid(lme21RQ5c , scaled = TRUE)) > 3) / length(resid(lme21RQ5c )) 

#2) Homoscedasticity
plot(lme21RQ5c, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5c, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5c_p <- afex::mixed(LowArousalPositiveAffectMean ~ LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +LowArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ5c_p


##high arousal positive affect##

#####fit mixed model#####
lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) #negative eigenvalue

lme21RQ5d <- lme4::lmer(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5))) #works

#get first summary
summary(lme21RQ5d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 2) / length(resid(lme21RQ5d ))
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ5d )) 
sum(abs(resid(lme21RQ5d , scaled = TRUE)) > 3) / length(resid(lme21RQ5d )) 

#2) Homoscedasticity
plot(lme21RQ5d, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ5d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ5d, scaled = TRUE))

#qqplot shows outliers in the tails


#Conclusion: There are some issues with the assumptions here. Proceed with caution.

#Calculate p-values

RQ5d_p <- afex::mixed(HighArousalPositiveAffectMean ~ HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch + (1 +HighArousalPositiveAffectMeanLaggedScaled*Alone*epoch || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE, optCtrl=list(maxfun=1e5)), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)
RQ5d_p
```

For all four analysis, Alone and the lagged affect variable emerge as significant predictors. Here, we are mainly interested in the effect of the lagged affect variables. Therefore, we correct for multiple testing for the effect of the lagged affect variables

### Correction for Multiple Testing

```{r RQ640mt, echo = TRUE}


#Adjust effect of affect.0 variables
df_analysis21RQ5.2_pvalues <- as.data.frame(rbind(RQ5_p$anova_table$`Pr(>F)`[2], RQ5b_p$anova_table$`Pr(>F)`[2], RQ5c_p$anova_table$`Pr(>F)`[2], RQ5d_p$anova_table$`Pr(>F)`[2]))

df_analysis21RQ5.2_pvalues$adjusted <- p.adjust(df_analysis21RQ5.2_pvalues$V1, method = "holm")
df_analysis21RQ5.2_pvalues$adjusted #all remain significant


```

All four p-values for the effect of the affect.0 variables remain significant even after correction for multiple testing.