# Sensitivity Analyses: 60%

In the next section we report the sensitivity analyses based on all participants with at least 60% correct responses.

```{r 60%prep, echo = TRUE}
df_analysis21 <- subset(df, df$Surveys.completed >= 21)

#scale independent continuous variables
df_analysis21$StructureForSolitudeIndividualScaled <- scale(df_analysis21$StructureForSolitudeIndividual)
df_analysis21$DayLevelIntentionalitySolitudeScaled <- scale(df_analysis21$DayLevelIntentionalitySolitude)
df_analysis21$DayLevelNatureScaled <- scale(df_analysis21$DayLevelNature)
df_analysis21$DayLevelStructureSolitudeScaled <- scale(df_analysis21$DayLevelStructureSolitude)

df_analysis21$Alone <- as.factor(as.character(df_analysis21$Alone))


df_analysis21_2 <- df_analysis21 %>% select(LowArousalNegativeAffectMean, LowArousalPositiveAffectMean, HighArousalNegativeAffectMean, HighArousalPositiveAffectMean, Alone)
```


## Research Question 1

### Hypothesis 1a
```{r 601a, echo = TRUE}
lme21RQ1d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> converges

#get first summary
summary(lme21RQ1d)




#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 2) / length(resid(lme21RQ1d ))
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1d )) 
sum(abs(resid(lme21RQ1d , scaled = TRUE)) > 3) / length(resid(lme21RQ1d )) 

#2) Homoscedasticity
plot(lme21RQ1d, type = c('p', 'smooth'))
#Looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1d, scaled = TRUE))

#Normal enough, but the qqplot some outliers in the tails, small problem

RQ1d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1d_p
#effect of alone significant
#positive estimate


by(df_analysis21_2,df_analysis21_2$Alone, summary)
#check contrasts to verify results
contrasts(df_analysis21$Alone) 

#Hypothesis 1A confirmed



```

Hypothesis 1a is also confirmed for the 60% sensitivity analyses.

### Hypothesis 1b

```{r 601b, echo = TRUE}
lme21RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21) # -> Singular Fit
#1) change to bobyqa
lme21RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) # -> Singular Fit
#2) Turn of gradient and hessian
lme21RQ1c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) # -> convergences


#get first summary
summary(lme21RQ1c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 2) / length(resid(lme21RQ1c )) 
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1c )) 
sum(abs(resid(lme21RQ1c , scaled = TRUE)) > 3) / length(resid(lme21RQ1c )) 

#2) Homoscedasticity
plot(lme21RQ1c, type = c('p', 'smooth'))
#Looks mostly fine, but strays quite far at the end

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1c, scaled = TRUE))

#Normal enough, but the qqplot shows a lot of outliers in the tails, which is quite problematic
#Calculate p-values
RQ1c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1c_p
#effect of alone not significant
#Hypothesis 1b not confirmed
```

Hypothesis 1b is not confirmed.

### Hypothesis 1c

```{r 601c, echo = TRUE}
lme21RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21) # -> Singular Fit
#1) Change to bobyqa
lme21RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> Singular Fit

#2) Turn of gradient and hessian
lme21RQ1b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> No Singular Fit warning

#get first summary
summary(lme21RQ1b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 2) / length(resid(lme21RQ1b )) 
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1b )) 
sum(abs(resid(lme21RQ1b , scaled = TRUE)) > 3) / length(resid(lme21RQ1b )) 

#2) Homoscedasticity
plot(lme21RQ1b, type = c('p', 'smooth'))
#Looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails

RQ1b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ1b_p 
#Effect of Alone is significant
by(df_analysis21_2,df_analysis21_2$Alone, summary)

#check contrasts to verify results
contrasts(df_analysis21$Alone) 

#Hypothesis 1C not confirmed, effect in the opposite direction.


```

Hypothesis 1C is not confirmed. In contrast, here the effect also goes into the opposite direction.

### Hypothesis 1d

```{r 601d, echo = TRUE}
lme21RQ1 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21)

#get first summary
summary(lme21RQ1)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 2) / length(resid(lme21RQ1 ))
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ1 ))
sum(abs(resid(lme21RQ1 , scaled = TRUE)) > 3) / length(resid(lme21RQ1 ))

#2) Homoscedasticity
plot(lme21RQ1, type = c('p', 'smooth'))
#Also somewhat violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ1, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ1, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
RQ1_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone + (1 + Alone | Participant.ID) + (1 | SubjDay), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)

#Hypothesis 1D is not supported.
RQ1_p


```

Hypothesis 1D is not supported.

### Correction for Multiple Testing

Next we check whether these effects also hold after correction for multiple testing.

```{r 60mt, echo = TRUE}

df_analysis21RQ1_pvalues <- as.data.frame(rbind(RQ1_p$anova_table$`Pr(>F)`, RQ1b_p$anova_table$`Pr(>F)`, RQ1c_p$anova_table$`Pr(>F)`, RQ1d_p$anova_table$`Pr(>F)`))

df_analysis21RQ1_pvalues$adjusted <- p.adjust(df_analysis21RQ1_pvalues$V2, method = "holm")
#only model 4 remains significant, hence 1A is also confirmed after correction, whereas the effect in the opposite direction at 1C disappears.

df_analysis21RQ1_pvalues$adjusted
```

Hypothesis 1a is confirmed after correction for multiple testing. The effect observed at 1C also remains significant after correction for multiple testing.

## Research Question 2

### Hypotheses 2Aa and 2Bc

```{r 602a, echo = TRUE}
lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges , but negative  eigenvalues

lme21RQ2d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 


#get first summary
summary(lme21RQ2d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 2) / length(resid(lme21RQ2d )) 
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2d )) 
sum(abs(resid(lme21RQ2d , scaled = TRUE)) > 3) / length(resid(lme21RQ2d )) 

#2) Homoscedasticity
plot(lme21RQ2d, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2d, scaled = TRUE))

#qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)
RQ2d_p 
#2Aa not supported. "Support" for 2Bc/d because we predicted no effect and there is no effect
#Significant effect of Alone
```

Hypothesis 2Aa is not supported. However, as expected, we find no significant interaction effect (2Bc)

### Hypotheses 2Ab and 2Bd

```{r 602Aa, echo = TRUE}

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalues

lme21RQ2c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 
#get first summary
summary(lme21RQ2c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 2) / length(resid(lme21RQ2c ))
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2c )) 
sum(abs(resid(lme21RQ2c , scaled = TRUE)) > 3) / length(resid(lme21RQ2c )) 

#2) Homoscedasticity
plot(lme21RQ2c, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2c, scaled = TRUE))

#Barely Normal and the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)
RQ2c_p 
#2Ab not supported. 2Bc/d "supported", as in we did not predict an effect and we did not observe an effect

```

Hypothesis 2Ab is not supported. However, as expected, we observed no interaction (2Bd).

### Hypotheses 2Ac and 2Ba

```{r 602Ac, echo = TRUE}
lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges and produces negative eigenvalues

lme21RQ2b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ2b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 2) / length(resid(lme21RQ2b )) 
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2b )) 
sum(abs(resid(lme21RQ2b , scaled = TRUE)) > 3) / length(resid(lme21RQ2b ))

#2) Homoscedasticity
plot(lme21RQ2b, type = c('p', 'smooth'))
#looks mostly fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2b, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone + DayLevelNatureScaled || Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster, expand_re = TRUE)
RQ2b_p
#2Ac and 2Ba not supported

```

Hypothesis 2Ac and hypothesis 2Ba are not supported.

### Hypotheses 2Ad and 2Bb

```{r 602Ad, echo = TRUE}

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ2 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ2)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 2) / length(resid(lme21RQ2 )) 
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ2 )) 
sum(abs(resid(lme21RQ2 , scaled = TRUE)) > 3) / length(resid(lme21RQ2 ))

#2) Homoscedasticity
plot(lme21RQ2, type = c('p', 'smooth'))
#Trails off strongly in the tails

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ2, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ2, scaled = TRUE))

#Normal enough, but the qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ2_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelNatureScaled + (1 + Alone*DayLevelNatureScaled | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR", test_intercept = TRUE, cl = MyCluster)
RQ2_p
#no significant hypothesized effects, 
#Hypothesis 2Ad and 2Bb not supported
```

Hypothesis 2Ad and hypothesis 2Bb are not supported.

## Research Question 3

### Hypotheses 3Aa and 3Bc

```{r 603Aa, echo = TRUE}

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #does not converge

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa"), data = df_analysis21) #does not converge

lme21RQ3d <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21) #converges

#get first summary
summary(lme21RQ3d)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 2) / length(resid(lme21RQ3d )) 
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3d ))
sum(abs(resid(lme21RQ3d , scaled = TRUE)) > 3) / length(resid(lme21RQ3d ))

#2) Homoscedasticity
plot(lme21RQ3d, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3d, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3d, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3d_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3d_p 

```

Hypothesis 3Aa is not supported. However, as expected, there is no interaction (3Bc).

### Hypotheses 3Ab and 3Bd

```{r 603ab, echo = TRUE}

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ3c <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges




#get first summary
summary(lme21RQ3c)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 2) / length(resid(lme21RQ3c )) 
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3c ))
sum(abs(resid(lme21RQ3c , scaled = TRUE)) > 3) / length(resid(lme21RQ3c ))

#2) Homoscedasticity
plot(lme21RQ3c, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3c, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3c, scaled = TRUE))

#qqplot shows quite some outliers in the tails


#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3c_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#3Ab not supported, 3Bc/d: No interaction
RQ3c_p 
```

Hypothesis 3Ab is not supported. However, as expected, we observed no interaction (3Bd).

### Hypotheses 3Ac and 3Ba

```{r 603Ac, echo = TRUE}

lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence
#remove interaction
lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but produces negative eigenvalue in p-value calculation
lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


lme21RQ3b <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone+DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) # -> converges and also afex likes it

#get first summary
summary(lme21RQ3b)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 2) / length(resid(lme21RQ3b ))
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3b )) 
sum(abs(resid(lme21RQ3b , scaled = TRUE)) > 3) / length(resid(lme21RQ3b ))

#2) Homoscedasticity
plot(lme21RQ3b, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3b, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3b, scaled = TRUE))

#qqplot shows some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3b_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone+DayLevelIntentionalitySolitudeScaled || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), expand_re = TRUE, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
RQ3b_p 
#3Ac and 3Ba not supported

```

Hypotheses 3Ac and 3Ba are not supported.

### Hypotheses 3Ad and 3Bb

```{r 603Ad, echo = TRUE}

lme21RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ3 <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges 


#get first summary
summary(lme21RQ3)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 2) / length(resid(lme21RQ3 )) 
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 2.5) / length(resid(lme21RQ3 )) 
sum(abs(resid(lme21RQ3 , scaled = TRUE)) > 3) / length(resid(lme21RQ3 )) 

#2) Homoscedasticity
plot(lme21RQ3, type = c('p', 'smooth'))
#skewed in the right tail

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ3, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ3, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ3_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelIntentionalitySolitudeScaled + (1 + Alone*DayLevelIntentionalitySolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#3Ad and 3Bb not supported
RQ3_p 
```

Hypotheses 3Ad and 3Bb are not supported.

## Research Question 4

### Hypotheses 4Aa and 4Ba Day-Level

```{r 604Aday, echo = TRUE}
llme21RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalues

lme21RQ4d.day <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ4d.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4d.day )) 
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4d.day ))
sum(abs(resid(lme21RQ4d.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4d.day )) 
#2) Homoscedasticity
plot(lme21RQ4d.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4d.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4d.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
RQ4d.day_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  expand_re = TRUE, cl = MyCluster)
#Hypothesis 4Aa and 4Ba day not supported
RQ4d.day_p 
```
Hypotheses 4Aa and 4Ba day-level are not supported.

### Hypotheses 4Ab and 4Bb Day-Level

```{r 604Abday, echo = TRUE}


lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ4c.day <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges



#get first summary
summary(lme21RQ4c.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4c.day ))
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4c.day )) 
sum(abs(resid(lme21RQ4c.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4c.day ))
#2) Homoscedasticity
plot(lme21RQ4c.day, type = c('p', 'smooth'))
#looks good

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4c.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4c.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails

#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ4c.day_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ab and 4Bb day not supported
RQ4c.day_p
```

Hypotheses 4Ab and 4Bb day-level are not supported.

### Hypotheses 4Ac and 4Bc Day-Level

```{r 604Acday, echo = TRUE}

lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not converge

#
lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), control = lmerControl(optimizer = "bobyqa"), data = df_analysis21) #-> does not converge


lme21RQ4b.day <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay),control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21) #-> converges


#get first summary
summary(lme21RQ4b.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4b.day )) 
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4b.day )) 
sum(abs(resid(lme21RQ4b.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4b.day )) 

#2) Homoscedasticity
plot(lme21RQ4b.day, type = c('p', 'smooth'))
#looks fine

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4b.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4b.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ4b.day_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay),control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), data = df_analysis21, type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ac day not supported, 4Bc/d: No Interaction
RQ4b.day_p

```

Hypothesis 4Ac day is not supported. However, as expected, there is no interaction (4Bc).

### Hypotheses 4Ad and 4Bd Day-Level

```{r 604Adday, echo = TRUE}

lme21RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #does not convergence

lme21RQ4.day <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ4.day)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 2) / length(resid(lme21RQ4.day ))
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4.day )) 
sum(abs(resid(lme21RQ4.day , scaled = TRUE)) > 3) / length(resid(lme21RQ4.day ))

#2) Homoscedasticity
plot(lme21RQ4.day, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4.day, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4.day, scaled = TRUE))

#qqplot shows quite some outliers in the tails

RQ4.day_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*DayLevelStructureSolitudeScaled + (1 + Alone*DayLevelStructureSolitudeScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ad day not supported, 4Bc/d: No Interaction
RQ4.day_p 
```

Hypothesis 4Ad day-level is not supported. However, as expected, there is no interaction (4Bd).

### Hypotheses 4Aa and 4Ba Person-Level

```{r 604aperson, echo = TRUE}
lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalues

lme21RQ4d.individual <- lme4::lmer(HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))

#get first summary
summary(lme21RQ4d.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4d.individual ))
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4d.individual ))  
sum(abs(resid(lme21RQ4d.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4d.individual ))

#2) Homoscedasticity
plot(lme21RQ4d.individual, type = c('p', 'smooth'))
#looks good
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4d.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4d.individual, scaled = TRUE))

#qqplot shows outliers in the tails

RQ4d.individual_p <- afex::mixed (HighArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa",  calc.derivs = FALSE), type = 3, method = "KR", expand_re = TRUE, test_intercept = TRUE,  cl = MyCluster)
RQ4d.individual_p
#Hypothesis 4Aa and 4Ba not suported
```

Hypotheses 4Aa and 4Ba person-level are not supported.

### Hypotheses 4Ab and 4Bb Person-Level

```{r 604Abperson, echo = TRUE}
lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4c.individual <- lme4::lmer(HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges




#get first summary
summary(lme21RQ4c.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4c.individual )) 
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4c.individual ))
sum(abs(resid(lme21RQ4c.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4c.individual )) 
#2) Homoscedasticity
plot(lme21RQ4c.individual, type = c('p', 'smooth'))
#looks slightly violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4c.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4c.individual, scaled = TRUE))

#qqplot shows strong outliers in the tails
#RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Fehler in h(simpleError(msg, call)) : 
#Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl für Funktion 'forceSymmetric': Lapackroutine dgesv: System ist genau singulär: U[12,12] = 0

RQ4c.individual_p <- afex::mixed (HighArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S",  cl = MyCluster)
RQ4c.individual_p 
```

Hypotheses 4Ab and 4Bb are not supported. 

### Hypotheses 4Ac and 4Bc Person-Level

```{r 604Acperson, echo = TRUE}
lme21RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but negative eigenvalues

lme21RQ4b.individual <- lme4::lmer(LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges


#get first summary
summary(lme21RQ4b.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4b.individual ))
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4b.individual ))  
sum(abs(resid(lme21RQ4b.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4b.individual ))

#2) Homoscedasticity
plot(lme21RQ4b.individual, type = c('p', 'smooth'))
#looks fine
#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4b.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4b.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#RQ4b.individual_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)

#Fehler bei der Auswertung des Argumentes 'x' bei der Methodenauswahl für Funktion 'forceSymmetric': System ist für den Rechner singulär: reziproke Konditionszahl = 1.80696e-16

RQ4b.individual_p <- afex::mixed (LowArousalPositiveAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  || Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "S",  cl = MyCluster, expand_re = TRUE)
RQ4b.individual_p
#Hypothesis 4Ac individual not supported, 4Bc/d: No Interaction
```

Hypothesis 4Ac person-level is not supported. However, there is no significant interaction (as expected 4Bc).

### Hypotheses 4Ad and 4Bd Person-Level

```{r 604adperson, echo = TRUE}

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21) #-> does not convergence

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa")) #-> does not convergence

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone*StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE)) #-> converges, but shows eigenvalue issues

lme21RQ4.individual <- lme4::lmer(LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone+StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE))

#get first summary
summary(lme21RQ4.individual)



#check assumptions
#1) Outliers
#proportion of residuals larger than +/- 2, 2.5, 3.
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 2) / length(resid(lme21RQ4.individual )) 
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 2.5) / length(resid(lme21RQ4.individual ))
sum(abs(resid(lme21RQ4.individual , scaled = TRUE)) > 3) / length(resid(lme21RQ4.individual ))

#2) Homoscedasticity
plot(lme21RQ4.individual, type = c('p', 'smooth'))
#looks violated

#3) Normality
#densityplot of the scaled residuals
densityplot(resid(lme21RQ4.individual, scaled = TRUE))
#qqplot of the scaled residuals
car::qqPlot(resid(lme21RQ4.individual, scaled = TRUE))

#qqplot shows quite some outliers in the tails
#Calculate p-values
#says the predictor is not centered on zero, but like 15 digits after the comma are 0s
RQ4.individual_p <- afex::mixed (LowArousalNegativeAffectMean ~ Alone*StructureForSolitudeIndividualScaled + (1 + Alone+StructureForSolitudeIndividualScaled  | Participant.ID) + (1 | SubjDay), data = df_analysis21, control = lmerControl(optimizer = "bobyqa", calc.derivs = FALSE), type = 3, method = "KR",test_intercept = TRUE,  cl = MyCluster)
#Hypothesis 4Ad individual not supported, 4Bc/d: No Interaction
RQ4.individual_p 
```

Hypothesis 4Ad person-level is not supported. Moreover, as expected, there was no interaction (4Ad).
